An Open and Continuously Updated Fern Tree of Life (FTOL)

### 2022-02-26 ms/manuscript.Rmd
WIP: add bs values

tar_load(
  c(
    accs_exclude,
    fern_sanger_seqs_raw,
    fossil_calibration_tips,
    monophy_by_clade,
    plastid_calibration_dates,
    plastid_tree_dated,
    plastome_alignment,
    plastome_alignment_tbl,
    plastome_metadata_raw_all,
    plastome_metadata_renamed,
    plastome_metadata_renamed,
    plastome_seqs_combined_filtered,
    plastome_tree,
    ppgi_taxonomy,
    pteridocat,
    raw_fasta_all,
    sanger_accessions_selection,
    sanger_alignment,
    sanger_alignment_tbl,
    sanger_con_tree_rooted,
    sanger_seqs_combined_filtered,
    sanger_seqs_rogues_removed,
    treepl_cv_results,
    ts_fossil_calibration_tips
  ),
  store = ftol_cache
)

# Targets from MS workflow
tar_load(
  c(
    accepted_species,
    sanger_sampling,
    coverage_by_rank,
    total_coverage,
    bb_coverage_by_rank,
    bb_total_coverage,
    gb_species_by_year,
    ref_files,
    other_dates,
    crown_ages,
    fossil_ferns_raw,
    family_stem_ages,
    fern_monophy_summ_tbl,
    fern_nonmono_gen,
    plastome_iqtree_log
  ),
  store = here::here("_targets")
)
```

>>>>

tar_load(
  c(
    accs_exclude,
    fern_sanger_seqs_raw,
    fossil_calibration_tips,
    monophy_by_clade,
    plastid_calibration_dates,
    plastid_tree_dated,
    plastome_alignment,
    plastome_alignment_tbl,
    plastome_metadata_raw_all,
    plastome_metadata_renamed,
    plastome_metadata_renamed,
    plastome_seqs_combined_filtered,
    plastome_tree,
    ppgi_taxonomy,
    pteridocat,
    raw_fasta_all,
    sanger_accessions_selection,
    sanger_alignment,
    sanger_alignment_tbl,
    sanger_con_tree_rooted,
    sanger_seqs_combined_filtered,
    sanger_seqs_rogues_removed,
    ts_fossil_calibration_tips
  ),
  store = ftol_cache
)

# Targets from MS workflow
tar_load(
  c(
    accepted_species,
    sanger_sampling,
    coverage_by_rank,
    total_coverage,
    bb_coverage_by_rank,
    bb_total_coverage,
    gb_species_by_year,
    ref_files,
    other_dates,
    crown_ages,
    fossil_ferns_raw,
    family_stem_ages,
    fern_monophy_summ_tbl,
    fern_nonmono_gen,
    plastome_iqtree_log,
    treepl_cv_results
  ),
  store = here::here("_targets")
)
```
